|

### 2025-11-27 manuscript/pre_print.qmd
add ama csl
Check rendering

csl: apa.csl

@@

@@

#

>>>>

csl: american-medical-association.csl

@@

```{r}
targets::tar_load(c(main_arm_mean_effects_contrast_condition_bmi, main_arm_mean_effects_contrast_condition_fat_free_mass))

@@

# Data Availability
All code utilised for data preparation, transformations, analyses, plotting, and reporting are available in the corresponding GitHub repository <https://github.com/jamessteeleii/pcos_ree_meta>.
